HO unification from object language to meta language

### 2024-03-24 paper/main.tex
more work on 5

\begin{invariant}[Link left hand side] The left hand side of a new link
  is a flexible term.
\end{invariant}

\marginpar{WARNING: not true if we delay beta}

@@

@@

In order to express properties \ref{prop:correct, prop:complete, prop:simulation}
we need to equip \Fo and \Ho with term equality,
substitution application and unification.

@@

The objective of the compilation is to recognize the higher-order variables
available in \Ho{} when expressed in a first order way in \Fo{}. The compiler
also generates a map to bring back the substitution from
\Ho{} to \Fo{}.

@@

This preliminary version of \elpiIn{comp} simply recognizes \Fo variables
applied to a (possibly empty) duplicate free list of names (i.e.
\elpiIn{pattern-fragment} detects variables in \llambda). Note tha compiling
\elpiIn{Ag} cannot create new mappings nor links, see the comp-lam hyp rule.

The auxiliary function \elpiIn{close-links}

@@

since we want links to bubble up we use the abs constructor of the inctx data
type to bind back the variable just crossed, and we do so only if the variable
v occurs in L.

@@

@@

>>>>

@@

\begin{invariant}[Link left hand side] The left hand side of a new link
  is a variable.
\end{invariant}

\noindent
If the variable is assigned during a run the link is considered for
progress and possibly eliminated. This is discussed in
section~\ref{sec:eta}.\marginpar{is this the right section?}

@@

In order to express properties \ref{prop:correct, prop:complete, prop:simulation}
we need to equip \Fo{} and \Ho with term equality,
substitution application and unification.

@@

The main task of the compiler is to recognize \Fo{} variables standing
for functions and map them to higher order variables in \Ho.
In order to bring back the substitution from \Ho{} to \Fo{} the compiler
builds a ``memory map'' connecting the the kind of variables using routine
\ref{clause:malloc}.

@@

\noindent
This preliminary version of \elpiIn{comp} recognizes \Fo{} variables
applied to a (possibly empty) duplicate free list of names (i.e.
\elpiIn{pattern-fragment} detects variables in \llambda). Note tha compiling
\elpiIn{Ag} cannot create new mappings nor links, since \elpiIn{Ag}
is made of bound variables and the hypothetical rule loaded by \elpiIn{comp-lam}
(see below) grants this property.

@@

\noindent
The auxiliary function \elpiIn{close-links} tests if the bound variable
\elpiIn{v} really occurs in the link. If it is the case the link is wrapped into
an additional \elpiIn{abs} node binding \elpiIn{v}. In this way links generated
deep inside the compiled terms can be moved outside their original context
of binders.

Note that \elpiIn{pi x y\..} is syntactic sugar for \elpiIn{pi x\ pi y\..}.

@@

XXX links are update unlike section 2
\input{code/hstep}

note \elpiIn{(a = b) c d} is \elpiIn{(=) a b c d}.

@@

\input{code/decomp}
\input{code/decompm}
